### 2017-09-09 paper/evaluation.tex
Adjusts on RQ7

To answer this research question, we selected 20 different subjects,

@@

test flakiness.
We used the sequential execution associated with each project as the
comparison baseline in this experiment.
We sorted the subjects by decreasing order of execution time and
selected the first 20 projects that uses JUnit 4.7 or later.
The rationale for this criteria is to ensure compatibility with
parallel configuration since older versions of JUnit does not support
parallel testing.
We ran each project on each configuration for \SubjectsReruns{} times.
Overall, we needed to reran test suites 360 times, 18 times (3x6

@@

observed in our measurements and the aggregated time cost of 360 test

>>>>

To answer this research question, we selected 15 different subjects,

@@

test flakiness.  We used the sequential execution associated with each
project as the comparison baseline in this experiment.  We sorted the
subjects by decreasing order of execution time and selected the first
15 projects that uses JUnit 4.7 or later.  The rationale for this
criteria is to ensure compatibility with parallel configuration since
older versions of JUnit does not support parallel testing.  We ran
each project on each configuration for \SubjectsReruns{} times.
Overall, we needed to reran test suites 270 times, 18 times (3x6

@@

observed in our measurements and the aggregated time cost of 270 test
